### 2025-04-21 evaluating-prediction-accuracy.qmd
20250419 - figure sizing
20250420 - cleanup

```{r}
library("petersenlab")
library("tidyverse")
library("pROC")
library("magrittr")
library("viridis")
library("viridisLite")
library("msir")
```

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

>>>>

```{r}
library("petersenlab")
library("pROC")
library("magrittr")
library("viridis")
library("viridisLite")
library("msir")
library("tidyverse")
```

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6
